Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-04 paper/main.tex
table

\newcommand{\mcolc}[2]{\multicolumn{#1}{c}{\bf #2}}
\begin{table*}[tb]
  \caption{Mean fitness (and standard deviation) of the best solution found. % at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. 
  Mean runtime is shown in hours. 
  %CEGO runs were stopped after 144 hours. This was the case for all LOP instances.
  \label{tab:results}}
  \resizebox{\textwidth}{!}{%
\begin{tabular}{r@{\hskip -2ex}*{5}{r}rl@{\hskip -2ex}*{3}{r}}
 \toprule
            &              & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the                                                                                                                                                                                                                                                                                           \\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack[r]{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){10-11}
\bf Problem & \bf Instance & \mcolc{2}{CEGO}              & \mcolc{2}{UMM}                                                                                                                                                                                                               &                                                          &           & \bf                       & \bf CEGO & \bf UMM \\\midrule
LOP         & N-p40-01     & 10496.6                      & (116.8)                                                                                                                                                                                                                      & 12369.1                                                  & (389.9)   & {[}-2157.1, -1587.9{]}    & 19.9     & 0.3     \\
LOP         & N-p40-02     & 11714.7                      & (84.7)                                                                                                                                                                                                                       & 13160.5                                                  & (454.8)   & {[}-1773.5, -1118.1{]}    & 20.1     & 0.3     \\
LOP         & N-t59b11xx   & 102408.0                     & (3800.2)                                                                                                                                                                                                                     & 114075.5                                                 & (5389.2)  & {[}-16084.2, -7250.8{]}   & 21.1     & 0.4     \\
LOP         & N-t59d11xx   & 12692.2                      & (1097.9)                                                                                                                                                                                                                     & 16662.9                                                  & (2155.3)  & {[}-5618.5, -2322.9{]}    & 21.2     & 0.4     \\
LOP         & N-p50-02     & 19090.5                      & (285.4)                                                                                                                                                                                                                      & 21746.6                                                  & (645.4)   & {[}-3140.6, -2171.6{]}    & 22.9     & 0.5     \\
LOP         & N-p50-01     & 18197.7                      & (225.6)                                                                                                                                                                                                                      & 21161.8                                                  & (657.4)   & {[}-3447.4, -2480.8{]}    & 23.2     & 0.5     \\
LOP         & N-sgb75.01   & 1893533.2                    & (28594.6)                                                                                                                                                                                                                    & 1992059.9                                                & (40235.7) & {[}-131577.1, -65476.3{]} & 33.2     & 1.0     \\
LOP         & N-sgb75.02   & 1895801.8                    & (82847.9)                                                                                                                                                                                                                    & 1967132.3                                                & (49228.1) & {[}-136421.2, -6239.8{]}  & 33.3     & 1.1     \\
PFSP        & rec05        & 1276.2                       & (15.1)                                                                                                                                                                                                                       & 1276.3                                                   & (8.4)     & {[}-11.8, 11.6{]}         & 18.3     & 0.1     \\
PFSP        & rec13        & 1992.9                       & (27.6)                                                                                                                                                                                                                       & 2057.8                                                   & (22.8)    & {[}-88.8, -41.0{]}        & 18.5     & 0.1     \\
PFSP        & rec19        & 2264.5                       & (45.0)                                                                                                                                                                                                                       & 2304.8                                                   & (37.7)    & {[}-79.4, -1.2{]}         & 18.2     & 0.2     \\
PFSP        & rec31        & 3415.5                       & (62.1)                                                                                                                                                                                                                       & 3419.3                                                   & (37.0)    & {[}-52.6, 45.0{]}         & 23.1     & 0.5     \\
\bottomrule
\end{tabular}}
\end{table*}

>>>>

\newcommand{\mcolc}[2]{\multicolumn{#1}{c}{\bf #2}}
\begin{table*}[tb]
  \caption{Mean fitness (and standard deviation) of the best solution found. % at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. 
  Mean runtime is shown in hours. 
  %CEGO runs were stopped after 144 hours. This was the case for all LOP instances.
  \label{tab:results}}
  \resizebox{\textwidth}{!}{%
\begin{tabular}{r@{\hskip 0ex}*{5}{r}rl@{\hskip -2ex}*{2}{r}}
 \toprule
            &              & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI of the                                                                                       \\mean difference}}} & \mcolc{2}{Mean runtime} \\\cmidrule(lr){3-6}\cmidrule(lr){9-10}
\bf Problem & \bf Instance & \mcolc{2}{CEGO}              & \mcolc{2}{UMM}                                                                  &           &           & \bf CEGO                  & \bf UMM    \\\midrule
LOP         & N-p40-01     & 10496.6                      & (116.8)                                                                         & 12369.1   & (389.9)   & {[}-2157.1,& -1587.9{]}    & 19.9 & 0.3 \\
LOP         & N-p40-02     & 11714.7                      & (84.7)                                                                          & 13160.5   & (454.8)   & {[}-1773.5,& -1118.1{]}    & 20.1 & 0.3 \\
LOP         & N-t59b11xx   & 102408.0                     & (3800.2)                                                                        & 114075.5  & (5389.2)  & {[}-16084.2,& -7250.8{]}   & 21.1 & 0.4 \\
LOP         & N-t59d11xx   & 12692.2                      & (1097.9)                                                                        & 16662.9   & (2155.3)  & {[}-5618.5,& -2322.9{]}    & 21.2 & 0.4 \\
LOP         & N-p50-02     & 19090.5                      & (285.4)                                                                         & 21746.6   & (645.4)   & {[}-3140.6,& -2171.6{]}    & 22.9 & 0.5 \\
LOP         & N-p50-01     & 18197.7                      & (225.6)                                                                         & 21161.8   & (657.4)   & {[}-3447.4,& -2480.8{]}    & 23.2 & 0.5 \\
LOP         & N-sgb75.01   & 1893533.2                    & (28594.6)                                                                       & 1992059.9 & (40235.7) & {[}-131577.1,& -65476.3{]} & 33.2 & 1.0 \\
LOP         & N-sgb75.02   & 1895801.8                    & (82847.9)                                                                       & 1967132.3 & (49228.1) & {[}-136421.2,& -6239.8{]}  & 33.3 & 1.1 \\
PFSP        & rec05        & 1276.2                       & (15.1)                                                                          & 1276.3    & (8.4)     & {[}-11.8,& 11.6{]}         & 18.3 & 0.1 \\
PFSP        & rec13        & 1992.9                       & (27.6)                                                                          & 2057.8    & (22.8)    & {[}-88.8,& -41.0{]}        & 18.5 & 0.1 \\
PFSP        & rec19        & 2264.5                       & (45.0)                                                                          & 2304.8    & (37.7)    & {[}-79.4,& -1.2{]}         & 18.2 & 0.2 \\
PFSP        & rec31        & 3415.5                       & (62.1)                                                                          & 3419.3    & (37.0)    & {[}-52.6,& 45.0{]}         & 23.1 & 0.5 \\
\bottomrule
\end{tabular}}
\end{table*}
